{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-10-15 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient With Error Bound Conditions gives Near Optimal Convergence Rate }}

@@

    \subsection{Optimizing the inexact proximal point problem}

@@

    In this section, we continue the discussion from \textcolor{red}{[REF PREVIOUS SECTION]}. 
    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon$. 

@@

            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$. 
            \item The primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 

@@

    \subsection{Conditions for linear convergence of the proximal problem}
        In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
        \end{proposition}
        \begin{proof}
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator function which represents a box constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also. 
            \par
            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
            \begin{align*}
                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
            \end{align*}
        \end{proof}
        \begin{remark}
            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 
        \end{remark}
        \par
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[inner loop linear convergence scenario I]\label{prop:inn-loop-lin-cnvg}

        \end{proposition}
        The following proposition characterizes another case where error bound conditions of problem problem holds. 
        \begin{proposition}[nonsmooth PLQ linear composite]\label{prop:plq-prox-problem}

        \end{proposition}
    \subsection{Inner loop complexity}
        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$. 
        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.

>>>>

\title{{
    \fontfamily{ptm}\selectfont 
    Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method
    }
}

@@

    \subsection{Optimizing the inexact proximal point problem}\label{sec:optz-inxt-pp-problem}

@@

    In this section, we continue the discussion from Section \ref{sec:optz-inxt-pp-problem}. 
    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon, B + \rho$ and $y_k$. 
    In this section, we will derive the sufficient conditions for linear convergence rate of the proximal gradient method can attain linear convergence rate for optimizing the dual formulation $\Psi_\lambda$ \eqref{eqn:dual-pp} of the proximal point problem. 

@@

            \item Assume function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$. 
            \item Assume the primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
            \item Assume $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 

@@

    \subsection{Conditions for linear convergence of the proximal problem}
        In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator function which represents a box constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also. 
            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[scenario I, 1-norm penalization]\label{prop:inn-loop-lin-cnvg}

        \end{proposition}
        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$. 
        \end{definition}
        The following proposition characterizes another case where error bound conditions of problem problem holds. 
        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}

        \end{proposition}
        \begin{proposition}[scenario II, convex PLQ linear composite]\label{prop:plq-prox-problem}

        \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}

        \end{example}
    \subsection{Inner loop complexity}
        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$. 
        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.
